---
title: "bar graph"
output:
  html_notebook: default
---

---


<!-- toc orderedList:0 depthFrom:1 depthTo:6 -->

* [Load data](#load-data)
* [Default barchart](#default-barchart)
* [Year labels](#year-labels)
* [Axis labels](#axis-labels)
* [Fill color and border](#fill-color-and-border)
* [Highlight USA colors](#highlight-usa-colors)
* [Highlight record years with color](#highlight-record-years-with-color)
* [Spacing](#spacing)
* [Main title](#main-title)

<!-- tocstop -->


# Load data
```{r}
hotdogs <- read.csv("data/hot-dog-contest-winners.csv", sep=",", header=TRUE)
```
# Default barchart
```{r}
barplot(hotdogs$Dogs.eaten)
```
# Year labels
```{r}
barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year)
```
# Axis labels
```{r}
barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year, xlab="Year", ylab="Hot dogs and buns (HDB) eaten")
```
# Fill color and border
```{r}
barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year, col="red", border=NA, xlab="Year", ylab="Hot dogs and buns (HDB) eaten")

```
# Highlight USA colors
```{r}
fill_colors <- c()
for ( i in 1:length(hotdogs$Country) ) {
	if (hotdogs$Country[i] == "United States") {
		fill_colors <- c(fill_colors, "#821122")
	} else {
		fill_colors <- c(fill_colors, "#cccccc")
	}
}
barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year, col=fill_colors, border=NA, xlab="Year", ylab="Hot dogs and buns (HDB) eaten")

```
# Highlight record years with color
```{r}
fill_colors <- c()
for ( i in 1:length(hotdogs$New.record) ) {
	if (hotdogs$New.record[i] == 1) {
		fill_colors <- c(fill_colors, "#821122")
	} else {
		fill_colors <- c(fill_colors, "#cccccc")
	}
}
barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year, col=fill_colors, border=NA, xlab="Year", ylab="Hot dogs and buns (HDB) eaten")

```
# Spacing
```{r}
barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year, col=fill_colors, border=NA, space=0.3, xlab="Year", ylab="Hot dogs and buns (HDB) eaten", main="Nathan's Hot Dog Eating Contest Results, 1980-2010")

barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year, col=fill_colors, border=NA, space=0.5, xlab="Year", ylab="Hot dogs and buns (HDB) eaten")
```
# Main title
```{r}
barplot(hotdogs$Dogs.eaten, names.arg=hotdogs$Year, col=fill_colors, border=NA, space=0.25, xlab="Year", ylab="Hot dogs and buns (HDB) eaten", main="Nathan's Hot Dog Eating Contest Results, 1980-2010")
```
